Figure 3 - ChIP

### 2024-08-06 ms_figure_3_chip.Rmd
add number of unique motifs to Facts and Numbers
transpose motif site barplot

@@

```{r plot-fracBound}
#| fig.width: 8
#| fig.height: 5

@@

(p_fracbound <- ggplot(pd, aes(fraction_bound, name, fill = peak_set)) +
        geom_col() +
        scale_x_continuous(expand = expansion(mult = 0),
                           labels = scales::label_percent()) +
        scale_fill_manual(values = peakset_colors) +
        labs(x = "Percent of motif sites",
             y = element_blank(),
             fill = element_blank()) +
        theme_cowplot(12) +
        theme(legend.position = "inside",
              legend.position.inside = c(0.95, 0.05),
              legend.justification.inside = c(1, 0),
              axis.text.y = element_text(angle = 0, hjust = 1, size = 8)) +
        guides(fill = guide_legend(ncol = 1)))
```

>>>>

# Number of unique motifs (based on manual classification)
sum(motifs$unique_version_of_motif)

@@

```{r plot-fracBound}
#| fig.width: 5
#| fig.height: 8

@@

(p_fracbound <- ggplot(pd, aes(name, fraction_bound, fill = peak_set)) +
        geom_col() +
        scale_y_continuous(expand = expansion(mult = 0),
                           labels = scales::label_percent()) +
        scale_fill_manual(values = peakset_colors) +
        labs(x = element_blank(),
             y = "Percent of motif sites",
             fill = element_blank()) +
        theme_cowplot(12) +
        theme(legend.position = "inside",
              legend.position.inside = c(0.05, 0.95),
              legend.justification.inside = c(0, 1),
              axis.text.x = element_text(angle = 90, hjust = 1, size = 8)) +
        guides(fill = guide_legend(ncol = 1)))
```
